News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-03-23 rupnik2015.tex
abstract

\begin{abstract}
Main points:
\begin{itemize}
\item Problem of tracking events in a large multilingual stream - we reduce it to event linking
\item Two contributions. We propose a method that enables cross-lingaul document similarity an approach to linking multilingual data and an approach that uses is to link events.
\item Evaluation of cross-lingual approaches on Wikipedia and the event linking task.
\end{itemize}

\end{abstract}
%\section{Overview}
%Structure
%\begin{itemize}
%\item Introduction
%\item Cross lingual document similarity (model)
%\item  Event Detection
%\item  Combing the approaches
%\item Experiments
%\item Conclusions
%\end{itemize}
%The story:
%\begin{itemize}
%\item Description of the problem - we would liek to understand events ans sequences of events, but our observables (e.g. news stories) occur in a variety of languages
%\item We present an approach to tackle this problem using a combination of techniques....
%\item Ultimately we present a tool showing the feasibility of our approach
%%\end{itemize}
%
%\section{Overview}
%Structure
%\begin{itemize}
%\item Introduction
%\item System overview
%\item Cross lingual document similarity (algorithms)
%\item Event linking
%\item Experiments
%\item Conclusions
%\end{itemize}
%The story:
%\begin{itemize}
%\item Description of the problem - we would like to understand global news as sequences of events, but our observables (e.g. news stories) occur in a variety of languages
%\item We present an approach to tackle this problem using a combination of techniques....
%\item Ultimately we present a tool showing the feasibility of our approach
%\end{itemize}
%

>>>>

\begin{abstract}
Today, we follow news  which is distributed globally and reported on in many different languages. When a significant event occurs, it is often reported on in many different sources. In this work, our goal is to consider the problem tracking events in a large multilingual stream. In this paper, we consider a particular aspect of this problem, namely how to link collections of articles in different languages which refer to the same event. Given a multi-lingual stream,  articles are first clustered according in each language we consider separately. Given these clusters, we first propose a  
method to enables cross-lingual document similarity based on Wikipedia, which
 enabling us to compute the similarity of any two articles regardless of language. Using this simliarity, we then propose an approach to find and match clusters across ;anguages which represent the same event. We provide an extensive evaluation of the performance of the system as a while as well as the quality of the similarity measure and linking algorithm. 
 \begin{comment}
Main points:
\begin{itemize}
\item Problem of tracking events in a large multilingual stream - we reduce it to event linking
\item Two contributions. We propose a method that enables cross-lingaul document similarity an approach to linking multilingual data and an approach that uses is to link events.
\item Evaluation of cross-lingual approaches on Wikipedia and the event linking task.
\end{itemize}
\end{comment}
\end{abstract}
%\section{Overview}
%Structure
%\begin{itemize}
%\item Introduction
%\item Cross lingual document similarity (model)
%\item  Event Detection
%\item  Combing the approaches
%\item Experiments
%\item Conclusions
%\end{itemize}
%The story:
%\begin{itemize}
%\item Description of the problem - we would liek to understand events ans sequences of events, but our observables (e.g. news stories) occur in a variety of languages
%\item We present an approach to tackle this problem using a combination of techniques....
%\item Ultimately we present a tool showing the feasibility of our approach
%%\end{itemize}
%
%\section{Overview}
%Structure
%\begin{itemize}
%\item Introduction
%\item System overview
%\item Cross lingual document similarity (algorithms)
%\item Event linking
%\item Experiments
%\item Conclusions
%\end{itemize}
%The story:
%\begin{itemize}
%\item Description of the problem - we would like to understand global news as sequences of events, but our observables (e.g. news stories) occur in a variety of languages
%\item We present an approach to tackle this problem using a combination of techniques....
%\item Ultimately we present a tool showing the feasibility of our approach
%\end{itemize}
%
